### 2020-03-20 ChapterImplementation/chapterImplementation.tex
Updated: Implementation includes chapter summary

>>>>

The implementation of AP will be discussed in this section. The following work is based on the implementation of AP used in \cite{brown2019aura}, however, with many newer additions. We include full details of the implementation of AP to give a complete and whole solution.

\section{Implementation Summary}
In this chapter the following points were discussed: 
\begin{itemize}
	\item The system architecture of AP, including how the servers are deployed in the cloud and how they communicate with a client.
	\item A breakdown of the components of each server.
	\item Topologies of server regions, including examples and the communication requirements between servers.
	\item Potential server deployments to be investigated in the future, such as the use of overseer nodes and dedicated render nodes for game streaming.
	\item A high-level description of the aura implementation including justifications for design decisions made.
	\item The algorithms used by the servers to implement AP.
	\item The life cycle of a simulated object as an FSM.
	\item The features and implementation details of the visualiser, including a description of its features and future work to be carried out on the visualiser.
\end{itemize}
